Parameter precision in economic growth models inspired by Ecological Economics

### 2015-10-05 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Fix to methods section.

Further complicating matters is our interest in issues that arise on the
boundary of (the economically meaningful portion of) the parameter space.
In an investigation of whether energy is important, for example,
we may consider the null hypothesis that $\alpha_3 = 0$.  
In the ($kl$)$e$ nesting for the CES model, 
this null hypothesis is equivalent to $\delta = 1$.
While there is an asymptotic theory for this case as well,%
  \authNote{Randy: can you provide a reference for the asymptotic theory? ---MKH}
the distributions are, in general,
more complicated---mixtures of chi-squared variates---and the
precise mix may be difficult or impossible to determine analytically.
\authNote{Ideally, we should check that there is not an easy analytical solution
in our particular case.  We'll see if there is time. ---rjp}%

>>>>

Further complicating matters is our interest in issues that arise on the
boundary of (the economically meaningful portion of) the parameter space.
In an investigation of the marginal productivity of energy 
in the $(kl)e$ nesting of the CES model, for example,
we may consider the null hypothesis that $\alpha_3 = 0$.  
This null hypothesis is equivalent to $\delta = 1$.
While there is an asymptotic theory for this case as well,%
  \authNote{Randy: can you provide a reference for the asymptotic theory? ---MKH}
the distributions are, in general,
more complicated---mixtures of chi-squared variates---and the
precise mix may be difficult or impossible to determine analytically.
\authNote{Ideally, we should check that there is not an easy analytical solution
in our particular case.  We'll see if there is time. ---rjp}%
